\textbf{Matching the forecast horizon with the relevant spatial and temporal processes and data sources}

### 2020-04-29 doc/response_2_reviews_Ecography1.txt

Recommendation by the Subject Editor (anonymous):

Both reviewers consider the work interesting and potentially highly valuable. I fully agree with them. The reason why your manuscript is rejected (with possibility to resubmit) was the the reviewers considered that the present version does not include sufficient information to truly evaluate the scientific contents (the analyses are basically not reproducible due to lacking information). Thus I urge you to pay specific attention to describe the methods in sufficient detail so that the results can be critically evaluated by the reviewers. Naturally, please address also all other comments provided by the two reviewers.

RESPONSE: Thank you for the opportunity to resubmit.  We have carefully addressed all of the reviewer's comments, making sure to add sufficient detail so that our results can be reproduced.

@@

Reviewer(s)' Comments to Author:
Reviewer: 1

Comments to the Author
The manuscript compares time series and a "space-for-time" approach for predicting species abundance and distribution in the future under two theoretical scenarios: meta-community dynamics and eco-evolutionary dynamics. The paper tackles an interesting and relevant question related to species distribution modeling and population assessment and provides some useful insight to it. The paper is well and clearly written.

My main concern with the paper is that it seems to exaggerate the importance and generality of its results. The abstract and introduction give impression that ecological forecast is tackled in very general manner. However, at the end authors study only two very simplistic (even though relavant) descriptions of ecological processes. Moreover, the set of statistical models compared is very narrow. Hence, the generality of their results is limited as well. This is not a weakness as such since with this simple example authors are able to show interesting results which are rather easily understandable. However, in my opinion the tone of the paper should be much more modest and authors should give relevant information about their simulation set up already in the abstract.

RESPONSE: We have rewritten the second half of the abstract to make it clear that all results come from two simple simulation studies. We also looked closely at the text in the Discussion to make sure we are not overselling our results. We think the revised version makes the limited scope of inference clear. As for the limited set of simple statistical models, that choice was intentional, as the reviewer recognizes. Because the statistical models are simple, they represent a wide variety of analogous models currently used in empirical research.

@@

I don't like the term "space-for-time". I have not encountered such term before and for me it is not informative. Why not use species distribution model or something similar that has already an established meaning.

RESPONSE: In our experience, "space-for-time" is a common term. A quick search on Google Scholar shows many papers with "space-for-time" in the title or abstract, including papers cited hundreds of times. Stuart Pickett's 1989 book chapter in the Long-term Studies in Ecology, titled, "Space-for-Time Substitution as an Alternative to Long-Term Studies," has been cited almost 1300 times (Google Scholar). "Species distribution model" is a narrower term, which does encompass other response variable, such as primary production. We wanted it to be clear that space-for-time approaches are not limited to species distribution models.

@@

In lines 150 and 152 authors use term "correlate". I know that statistical models are often called correlative models in ecology but it is typically wrong and at least impresice. Hence, I would describe in more detail how the model inference was done - maximum likelihood, Bayesian inference or least squares or what.

RESPONSE: We replaced "correlated" with regressed. Details on the regression models are provided in Appendix A.

The description of the simulation study should include the specific values used for the simulator. Authors should also tell more clearly are their results from single simulation or from several simulations. Moreover, it would be good to know how sensitive the results are to the chosen simulator parameters. That is, if the simulated dynamics was made faster/slower and the interspecific interactions and dispersal made stronger/weaker how would the results change. This kind of "sensitivity" test would provide information about the generality of the results and insight on for which kind of real systems they might apply.

RESPONSE:
Both reviewers raised concerns about the lack of sensitivity analyses and the robustness of our results. We take these concerns seriously and have responded in a number of ways. 	1) We added new material and references to the Introduction to emphasize that our simulations are motivated by empirical examples in which spatial and temporal models detect different relationships between an environmental driver and an ecological response. Any difference in magnitude or sign in these relationships will lead to contrasting forecasts. This situation appears quite frequently in the empirical literature; it is not a theoretical curiosity. The purpose of our simulations is not to convince readers that this situation might possibly occur (we already know it does), but rather to demonstrate how this situation may arise and the challenges and opportunities it presents for ecological forecasting. Given the generality of the motivating empirical pattern, the fact that we designed our case study to reproduce that pattern, and the fact that the signal to noise ratio in our deterministic simulations is high (only temperature is stochastic), we do not believe that a detailed sensitivity analysis is necessary. However, we do agree with the reviewer that understanding how different parameters influence the rate of the shift in model weights is an important goal for future research. Fig. 6 seeks to make that point, but a more rigorous analysis is beyond the scope of this study.
	2) We have added supplementary tables showing parameter values for both case studies. 
	3) We now clarify that the main text presents the results based on a single simulation run, but our results are qualitatively consistent for other runs.
	4) We have added more detail to the meta-community model description in Appendix B. We believe the description of the evo-evo model is quite complete (Appendix C), but would be happy to add more detail in response to specific questions. 
	5) We addressed Reviewer 2's question about nonstationarity (see below).

### 2020-04-29 doc/manuscript.tex
finishing revisions

\section*{Abstract} 
Most phenomenological, statistical models used to generate ecological forecasts take either a time-series approach, based on long-term data from one location, or a space-for-time approach, based on data describing spatial patterns across environmental gradients. \new{However, the magnitude and even the sign of environment-response relationships detected using these two approaches often differs, leading to contrasting predictions about responses to future environmental change.} Here we consider how the forecast horizon determines whether more accurate predictions come from the time-series approach, the space-for-time approach, or a combination of the two. We use two simulated case studies to show that forecasts for short and long forecast horizons need to focus on different ecological processes, which are reflected in different kinds of data. In the short-term, dynamics reflect initial conditions and fast processes such as birth and death, and the time-series approach makes the best predictions. In the long-term, dynamics reflect the additional influence of slower processes such as evolutionary and ecological selection, colonization and extinction, which the space-for-time approach can effectively capture. At intermediate time-scales, a weighted average of the two approaches shows promise. However, making this weighted model operational will require new research to predict the rate at which slow processes begin to influence dynamics.

@@

Conservation biologists and natural resource managers often need to anticipate the impact of environmental change on the abundance of 
endangered species, biological invaders, and harvested species. Although the managers may be primarily interested in just one focal species, skillful prediction might require considering interactions with many other species, greatly complicating the problem. But at what forecast horizon do altered species interactions become impossible to ignore? We explored this question using a metacommunity simulation model developed by \cite{alexander_lags_2018} to study how community responses to increasing temperature depend on the interplay between within-site demography and competitive interactions and the movement of species across sites. The model features Lotka-Volterra competitive interactions among plants within sites that are arrayed along an elevation and temperature gradient. Composition varies along the gradient because of a trade-off between growth rate and cold tolerance: cold sites are dominated by slow-growing species that can tolerate low temperatures, while warm sites are dominated by  fast-growing species that are cold intolerant. Multiple species can coexist within sites because all species experience stronger competition from conspecifics than from heterospecifics. Sites are linked by dispersal: a specified fraction of each species' offspring leaves the site where they were produced and reaches all other sites with equal probability. We provide a more detailed description of the simulation model in SI Appendix \ref{metacomm}. \new{Parameter values for the simulations described here in the main text are shown in Table \ref{tab:comm-turn-pars}.}

@@

@@

Evolutionary adaptation is a key uncertainty in predicting how environmental change will impact a focal population at a given location \citep{Hoffmann2011}. Like the shifts in species composition illustrated in the previous example, shifts in genotype frequencies can also influence dynamics and forecasts at different time scales. Although shifts in genotype frequencies at the population level are analogous to changes in species composition at the community level, the mechanisms are distinct: heterozygosity and genetic recombination have no analogue at the community level. We demonstrate how these processes influence short and long-term forecasts with a standard eco-evolutionary simulation model for a hypothetical annual plant population in which fecundity is temperature dependent, and different genotypes have different temperature optima (Fig. \ref{fig:evo_evo_spatial_temporal_models}A). All seeds germinate every year, preventing a seedbank from developing.

Our model describes how the local density of each genotype changes between years, which depends on temperature and genotype densities in the previous year. Transient temporal dynamics are computed directly from the model; these dynamics are the basis for the temporal statistical model. To create a spatial gradient, we simulated the equilibrium density of each genotype in a series of local populations experiencing different mean temperatures. The pattern of equilibrium densities across the mean annual temperature gradient is the basis for our spatial statistical model: cold sites will be dominated by the cold-adapted homozygous genotype, warm sites will be dominated by the heat-adapted homozygous genotype, and intermediate sites will be dominated by the heterozygous genotype (Fig. \ref{fig:evo_evo_spatial_temporal_models}B). The full description of the eco-evolutionary simulation model is provided in SI Appendix \ref{eco-evo}, and \new{parameter values for simulations described here are shown in Table \ref{tab:eco-evo-pars}. As in the first case study, we report results from just one simulation run, but results were qualitatively consistent for replicate runs.}

>>>>

\section*{Abstract} 
Most phenomenological, statistical models used to generate ecological forecasts take either a time-series approach, based on long-term data from one location, or a space-for-time approach, based on data describing spatial patterns across environmental gradients. However, the magnitude and even the sign of environment-response relationships detected using these two approaches often differs, leading to contrasting predictions about responses to future environmental change. Here we consider how the forecast horizon determines whether more accurate predictions come from the time-series approach, the space-for-time approach, or a combination of the two. We use simulated case studies to show that forecasts for short and long forecast horizons need to focus on different ecological processes, which are reflected in different kinds of data. First, we simulated population or community dynamics under stationary temperature using two simple, mechanistic models. Second, we fit statistical models to the simulated data using a time-series approach, a space-for-time approach, or a weighted average. We then forecast the response to a temperature increase using the statistical models, and compared these forecasts to temperature effects simulated by the mechanistic models. We found that the time-series approach made accurate short-term predictions because it captured initial conditions and effects of fast processes such as birth and death. The space-for-time approach made more accurate long-term predictions because it better captured the influence of slower processes such as evolutionary and ecological selection. The weighted average made accurate predictions at all time scales, including intermediate time-scales where the other two approaches performed poorly. A weighted average of time-series and space-for-time approaches shows promise, but making this weighted model operational will require new research to predict the rate at which slow processes begin to influence dynamics.

@@

Conservation biologists and natural resource managers often need to anticipate the impact of environmental change on the abundance of 
endangered species, biological invaders, and harvested species. Although the managers may be primarily interested in just one focal species, skillful prediction might require considering interactions with many other species, greatly complicating the problem. But at what forecast horizon do altered species interactions become impossible to ignore? We explored this question using a metacommunity simulation model developed by \cite{alexander_lags_2018} to study how community responses to increasing temperature depend on the interplay between within-site demography and competitive interactions and the movement of species across sites.

\subsection*{Methods}

The model features Lotka-Volterra competitive interactions among plants within sites that are arrayed along an elevation and temperature gradient. Composition varies along the gradient because of a trade-off between growth rate and cold tolerance: cold sites are dominated by slow-growing species that can tolerate low temperatures, while warm sites are dominated by  fast-growing species that are cold intolerant. Multiple species can coexist within sites because all species experience stronger competition from conspecifics than from heterospecifics. Sites are linked by dispersal: a specified fraction of each species' offspring leaves the site where they were produced and reaches all other sites with equal probability. We provide a more detailed description of the simulation model in SI Appendix \ref{metacomm}. \new{Parameter values for the simulations described here in the main text are shown in Table \ref{tab:comm-turn-pars}.}

@@

\subsection*{Results}

@@

Evolutionary adaptation is a key uncertainty in predicting how environmental change will impact a focal population at a given location \citep{Hoffmann2011}. Like the shifts in species composition illustrated in the previous example, shifts in genotype frequencies can also influence dynamics and forecasts at different time scales. Although shifts in genotype frequencies at the population level are analogous to changes in species composition at the community level, the mechanisms are distinct: heterozygosity and genetic recombination have no analogue at the community level. We demonstrate how these processes influence short and long-term forecasts with a standard eco-evolutionary simulation model for a hypothetical annual plant population.

\subsection*{Methods}

Our model assumes that fecundity is temperature dependent, and different genotypes have different temperature optima (Fig. \ref{fig:evo_evo_spatial_temporal_models}A). All seeds germinate every year, preventing a seedbank from developing. The model describes how the local density of each genotype changes between years, which depends on temperature and genotype densities in the previous year. Transient temporal dynamics are computed directly from the model; these dynamics are the basis for the temporal statistical model. To create a spatial gradient, we simulated the equilibrium density of each genotype in a series of local populations experiencing different mean temperatures. The pattern of equilibrium densities across the mean annual temperature gradient is the basis for our spatial statistical model: cold sites will be dominated by the cold-adapted homozygous genotype, warm sites will be dominated by the heat-adapted homozygous genotype, and intermediate sites will be dominated by the heterozygous genotype (Fig. \ref{fig:evo_evo_spatial_temporal_models}B). The full description of the eco-evolutionary simulation model is provided in SI Appendix \ref{eco-evo}, and \new{parameter values for simulations described here are shown in Table \ref{tab:eco-evo-pars}. As in the first case study, we report results from just one simulation run, but results were qualitatively consistent for replicate runs.}
